---
title: "Data EDA"
author: Yuri Matheus Dias Pereira
date: "`r format(Sys.time(), '%d/%m/%Y')`"
output: github_document
---

This a Notebook for an Exploratory Data Analysis on the Satellite telemetry data.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setuplibs}
library(tidyverse) # meta-package: everything else
library(data.table) # Table
library(lubridate) # Date
library(GGally) # ggplot2 convenience
library(parallel) # Threads counts
library(fst) # File reading
library(gridExtra) # Plot grids
```

# Reading the Data

Let's import the prepared telemetries description table now, along with some useful functions and constants defined in `reading_telemetry.R`:

```{r data}
root.dir <- "../"
source(paste0(root.dir, "R/reading_telemetry.R"))
DATA_DIR <- paste0(root.dir, "Data/")
TELEMETRY_FST_PATH <- paste0(DATA_DIR, "sat2_2018-03.fst")
sat2_TELEMETRIES_DESC_FILE <- paste0(DATA_DIR, "telemetryDescription.csv")

telemetries <- read.telemetries.description(sat2_TELEMETRIES_DESC_FILE)
sat2 <- read.telemetry.fst(TELEMETRY_FST_PATH)
```

This file will prove really useful, however...
```{r}
allTelemetries <- telemetries[, ID]
observedTelemetries <- names(sat2[,-c('date', 'CheckCRC')])
extraTelemetries <- observedTelemetries[
  !observedTelemetries %in% allTelemetries
]
extraTelemetries
```
This indicates that we have observed telemetries that are different from the actual documentation of the satellite.

Let's see how it looks like:
```{r}
telemetries[,.(.N), by = .(SYSTEM, EQP)]
```

All right, this should be enough importing for now.

# Some explorations

Get only the numerical variables for now.
```{r}
sat2.num <- sat2[, lapply(sat2, is.numeric) == TRUE, with = FALSE]
numericalTelemetries <- names(sat2.num)
```

From the sat2's official documents, we can select some interesting telemetries that follow true numerical examples:
```{r}
trueNumericalTelemetries <- c(
  'TM003','TM004','TM005','TM006','TM007','TM008'
)
```

Melts the data to make it boxplot-friendly.

```{r, fig.width=10,fig.height=30}
sat2.melt <- melt.data.table(
  sat2, id.vars = 'date', variable.name = 'series',
  measure.vars = trueNumericalTelemetries
)
ggplot(
  data = sat2.melt,
  aes(x = series, y = value, colour = series)
) +
  geom_boxplot() +
  coord_flip()
```

Following the manual, the TM3,4 and 5 are directly related to TM's 6,7 and 8, however I can't discern the difference between them like this. So we might need a correlation plot between these three variables.

Let's use the `ggcorr` functions:

```{r}
ggcorr(sat2.num[,..trueNumericalTelemetries])
```
As expected, these telemetries serve the same purpose, so it's no wonder that they're with a solid positive correlation. Let's see which one of these we can use for later analysis.

## Battery

Let's take a look on the battery subsystem:
```{r}
# TODO: use the converted telemetry table
batteryTelemetries <- c(
  'TM072','TM074','TM075','TM079','TM080','TM081'
)
sat2.melt <- melt.data.table(
  sat2, id.vars = 'date', variable.name = 'series',
  measure.vars = batteryTelemetries
)
ggplot(
  data = sat2.melt,
  aes(x = date, y = value, colour = series)
) +
  geom_line() +
  facet_grid(series ~ .)
```

Some noise is generated at the beginning and at the end of the passage...

Let's take a closer look on 81 and 72's data, since that they appear to have a greater variability.
```{r}
# TODO: use the converted telemetry table
batteryTempTelemetries <- c('TM072','TM081')
sat2.melt <- melt.data.table(
  sat2, id.vars = 'date', variable.name = 'series',
  measure.vars = batteryTempTelemetries
)
ggplot(
  data = sat2.melt,
  aes(x = date, y = value, colour = series)
) +
  #scale_y_log10() +
  geom_line()
```

This is simply messy. What's with all the outliers? Impossible to know anything from this graph. Let's try to zoom in...

> Query to know the noise

```{r}
firstPassageTime <- sat2[, date][1] %>%
  interval(end = sat2[, date][1336]) # Magic number
int_length(firstPassageTime)
sat2.firstPassage <- sat2[1:1336]
```
Just ad-hoc, better algorithm later...!

```{r}
sat2.melt <- melt.data.table(
  sat2.firstPassage, id.vars = 'date', variable.name = 'series',
  measure.vars = batteryTempTelemetries
)
ggplot(
  data = sat2.melt,
  aes(x = date, y = value, colour = series)
) +
  geom_line()
```

This is ok as an exercise, I guess, but I need to aggregate per passage....

Let's check the correlation:

```{r}
sat2[,..batteryTempTelemetries] %>% ggcorr()
```
Well, at least this one is as expected.

## Extra

What about the "extra" telemetries from before? What do they mean?

```{r}
sat2.extra <- sat2[,..extraTelemetries]
summary(sat2.extra)
```

Looks like 352 and 355 aren't being used in any way... let's focus on 353 and 354, then.
```{r}
sat2.extra[, c('TM352','TM355') := NULL]
summary(sat2.extra)
```

```{r}
sat2.melt <- melt.data.table(
  sat2, id.vars = 'date', variable.name = 'series',
  measure.vars = names(sat2.extra)
)
ggplot(
  data = sat2.melt,
  aes(x = date, y = value, colour = series)
) +
  geom_point() +
  scale_x_datetime(date_breaks = "1 day", date_labels = '%d-%m') +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  facet_grid(series ~ .)
```

## Discrete variables

Let's try and see the discrete variables this time

```{r}
sat2.disc <- sat2[, lapply(sat2, is.factor) == TRUE, with = FALSE]
discreteTelemetries <- names(sat2.disc)
```

```{r, fig.width=10,fig.height=30, s}
sat2.melt <- melt.data.table(
  sat2, id.vars = 'date', variable.name = 'series',
  measure.vars = discreteTelemetries
)
ggplot(
  data = sat2.melt,
  aes(value, colour = series)
) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  facet_wrap(~ series, ncol = 6, scales = 'free')
```

## Passages algorithm

A quick-and-dirty algorithm for adding passages numbers.
I am to blame for the $\mathcal{O}(n)$!

*UPDATE:* This is horribly slow, so I saved the results beforehand:

```{r}
sat_PASSAGES_FILE = paste0(DATA_DIR, '/sat2_2018-03-passages.fst')
sat2.passages <- read.fst(sat_PASSAGES_FILE, as.data.table = TRUE)
sat2 <- sat2[,passage := sat2.passages$passage]
```

Let's check them!

```{r}
sat2.melt <- melt.data.table(
  sat2, id.vars = 'date', variable.name = 'series',
  measure.vars = c('passage')
)
ggplot(
  data = sat2.melt,
  aes(value, colour = series)
) +
  geom_bar() +
  geom_hline(aes(yintercept = mean(value)), color = "blue")
```

This doesn't tell us much, though. Let's at least try to group by passages.

```{r}
sat2.melt <- sat2 %>%
  group_by(passage) %>%
  summarise(duration = (last(date) - first(date)))

ggplot(
  data = sat2.melt,
  aes(duration, colour = passage)
) +
  geom_histogram() +
  geom_vline(aes(xintercept = mean(duration)), col = 'red') +
  geom_vline(aes(xintercept = median(duration)), col = 'blue')
```

There's.... definitely something wrong with this algorithm.

```{r}
above.mean.passages <- sat2.melt %>%
  filter(duration >= median(duration))

above.75th.percentle.passages = sat2.melt %>%
  filter(duration >= 6.000000)

ggplot(
  data = sat2.melt,
  aes(x = passage, y = duration)
) +
  geom_point() +
  geom_quantile()
```

## CRC Check

This is a way for the system to know if the current telemetry frame was received properly.
It uses a simple bit-adding mechanism to know if the data is as expected, however, it can inform if the data is bad, and not correct it.
It's used because it's fast and simple, and missing a telemetry frame or two isn't apparently a big thing.
Also, it can happen depending on various telecommunication factors that aren't relevant here.

Let's get a visual for it...

```{r}
summary(sat2$CheckCRC)
#match('CheckCRC', names(sat2))
ggplot(
  data = sat2,
  aes(CheckCRC)
) +
  geom_bar()
```

Hmm... this might be the skew in the previous data. Let's make a small check for it.

```{r}
sat2.valid <- sat2[CheckCRC != 'Erro']

sat2.melt <- melt.data.table(
  sat2.valid, id.vars = 'date', variable.name = 'series',
  measure.vars = names(sat2.extra)
)
ggplot(
  data = sat2.melt,
  aes(x = date, y = value, colour = series)
) +
  geom_point() +
  scale_x_datetime(date_breaks = "1 day", date_labels = '%d-%m') +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  facet_grid(series ~ .)
```

This looks slighly better. Some of the odd values have disappeared, which supports the decision to take out the CRC checks altogether.

I do have one question, though: when are these checks most likely to appear?
```{r}
sat2.melt <- melt.data.table(
  sat2, id.vars = 'date', variable.name = 'series',
  measure.vars = c('CheckCRC')
)
ggplot(
  data = sat2.melt,
  aes(x = date, y = value, colour = series)
) +
  geom_jitter() +
  scale_x_datetime(date_breaks = "1 day", date_labels = '%d-%m') +
  theme(axis.text.x = element_text(angle = 60, hjust = 1))
```
... question not answered...

Let's group by week to check the distribution.
```{r}
sat2.melt <- melt.data.table(
  sat2, id.vars = 'date', variable.name = 'series',
  measure.vars = c('CheckCRC')
)

sat2.weeks <- sat2.melt %>%
  group_by(week = week(date), value) %>%
  summarise(count = n())

ggplot(
  data = sat2.weeks,
  aes(x = week, y = count, fill = value)
) +
  scale_y_log10() +
  geom_col(position = 'dodge')
```
Since this is log-scale, it just tells us that there's far less errors than OK values, as expected.
Without the log, this would get ugly and not so easy to see.
