---
title: "Data Codebook"
author: Yuri Matheus Dias Pereira
date: "`r format(Sys.time(), '%d/%m/%Y')`"
output: github_document
---

# Codebook

This a Notebook to explain how the telemetry data was formatted and saved.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup}
library(tidyverse)
library(data.table)
library(lubridate)
library(GGally)
library(parallel)
library(fst)
```

# Reading the Data

Some useful constants
```{r setup}
sat_DATA_FILE <- "./Data/sat2_2018-03.unix.csv"
CSV_SEPARATOR <- ","
```

Using `data.table`, for comparison.
```{r}
headerNames <- scan(
  file = sat_DATA_FILE,
  nlines = 1,
  what = character(),
  sep = CSV_SEPARATOR
) # Ignores first row as header names
headerDescription <- scan(
  file = sat_DATA_FILE,
  skip = 1,
  nlines = 1,
  what = character(),
  sep = CSV_SEPARATOR
)
headerUnits <- scan(
  file = sat_DATA_FILE,
  skip = 2,
  nlines = 1,
  what = character(),
  sep = CSV_SEPARATOR
)
```

```{r}
sat2 <- fread(
  input = paste("head -n -1", sat_DATA_FILE), # Ignores last row
  header = FALSE,
  #verbose = TRUE, # For debug
  skip = 3,
  encoding = 'Latin-1',
  dec = '.',
  nThread = detectCores(),
  stringsAsFactors = TRUE,
  check.names = TRUE,
  col.names = headerNames,
  sep = CSV_SEPARATOR
)
sat2 <- sat2[,.SD[-1:-2]] # Drops first two rows (desc and type)
#str(sat2)
```
It looks like the last row has a problem with it, of not having all the necessary data... but we're ignoring it for now.
```{r}
sat2[,`Data-Hora` := dmy_hms(`Data-Hora`)] %>%
  setnames("Data-Hora", "date")
# Lubridate makes this useless, here as comment
# as.POSIXct(strptime(`Data-Hora`, "%d-%b-%Y %H:%M:%OS"))
# Prints with fractional seconds
op <- options(digits.secs = 3)
str(sat2$date)
```

Let's import the prepared telemetries description table now.
```{r}
sat2_TELEMETRIES_DATA_FILE <- "./Data/telemetryDescription.csv"
telemetries <- fread(
  input =  sat2_TELEMETRIES_DATA_FILE,
  header = TRUE,
  #verbose = TRUE, # For debug
  encoding = 'Latin-1',
  dec = '.',
  nThread = detectCores(),
  stringsAsFactors = FALSE,
  check.names = TRUE,
  sep = CSV_SEPARATOR
)
```

Fast starter: already did everything above, just saved to .fst:
```{r}
TELEMETRY_FST_PATH <- "./Data/sat2_2018-03.fst"
sat2 <- read.fst(TELEMETRY_FST_PATH, as.data.table = TRUE)
```

This file will prove really useful, however...
```{r}
allTelemetries <- telemetries[, .(ID)]
observedTelemetries <- names(sat2[,-c('date', 'CheckCRC')])
extraTelemetries <- observedTelemetries[
  !observedTelemetries %in% allTelemetries
]
extraTelemetries
```
This indicates that we have observed telemetries that are different from the actual documentation of the satellite...

Let's see how it looks like:
```{r}
telemetries[,.(.N), by = .(SYSTEM, EQP)]
```

All right, this should be enough importing for now.

Get only the numerical variables for now.
```{r}
sat2.num <- sat2[, lapply(sat2, is.numeric) == TRUE, with = FALSE]
numericalTelemetries <- names(sat2.num)
```
